### 2021-02-09 final_report/include/Introduction.tex
added par on grammatical objects to the intro

% contribution (+ sw deliverables w technologies involved)
With this thesis, we propose a syntax-based approach to both of the above mentioned variants of CA - concept extraction and concept propagation - and put it to the test by integrating it in a prototype domain-specific MT system composed of a neural Universal Dependencies (UD) parser, a rule-based alignment module and a target language generation component based on Grammatical Framework (GF).

>>>>

Last but not least, a syntax-based approach can produce correspondences between grammatical objects, as opposed to pairs of strings. Alignments of this kind are valuable, as they can more easily be utilized in rule-based MT systems. \smallskip

% contribution (+ sw deliverables w technologies involved)
With this thesis, we propose a syntax-based approach to both of the above mentioned variants of CA - concept extraction and concept propagation - composed of a neural Universal Dependencies (UD) parser and a rule-based alignment module.
We put our system to the test by integrating it in a prototype domain-specific MT system based on Grammatical Framework (GF).
